---
title: "Alcohol vs Seat choice"
author: "Keren Gonzalez"
date: "Fall 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??


## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

Visually, there is a big difference between the back row and the middle row. There is also a much larger difference between the front and the back row.

## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=ucdavis1)
```

According to the table, the back row drinks 8.55 more drinks versus the middle row that drinks 3.33 drinks per week. Both of them drink more than the front row, which averages about 1.78 drinks per week. We can assume they are not drinking the same amount.

## Inferential Tests

## Conclusions


